Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-16 ms.qmd
model update. Fixed up VR figure

  # Lets now convert these to a %
    f_VR_mean_ef  <- abs((exp(f_VR_mean) - 1)*100) # ~8.4% reduction
    m_VR_mean_ef  <- abs((exp(m_VR_mean) - 1)*100) # ~15% reduction
    t_VR_mean_ef  <- abs((exp(t_VR_mean) - 1)*100) # ~30% reduction

@@

##################
  # Figure S1
################## 
  # Sensitivity analysis that looks at how variance changes but not controlling for the mean.
  col <- c("#0871B9", "#F3B40D", "#1BB908")
  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", data = lnVRQ10_data, angle = 45, trunk.size = 5) +
              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -5.2, 
           label =TeX(paste0("$\\mu = $", round(mean(f_VR_mean), 2), " [", round(quantile(f_VR_mean, 0.025), 2)," to ", round(quantile(f_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
  annotate("text", x = 1.15, y = -3.7, label = paste0("P = ", round(pmcmc(f_VR_mean), digit = 2)), hjust = 0, size = 6) + 
  annotate("text", x = 1.15, y = -5, 
           label =paste0(round(mean(exp(f_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + 
  annotate("text", x = 2.3, y = -5.2, 
           label =TeX(paste0("$\\mu = $", round(mean(m_VR_mean), 2), " [", round(quantile(m_VR_mean, 0.025), 2)," to ", round(quantile(m_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
  annotate("text", x = 2.15, y = -3.7, label = paste0("P = ", round(pmcmc(m_VR_mean), digit = 2)), hjust = 0, size = 6) + 
  annotate("text", x = 2.15, y = -5, 
           label =paste0(round(mean(exp(m_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + annotate("text", x = 3.3, y = -5.2, 
           label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
  annotate("text", x = 3.15, y = -5, 
           label =paste0(round(mean(exp(t_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
    annotate("text", x = 3.15, y = -3.7, label = paste0("P = ", round(pmcmc(t_VR_mean), digit = 3)), hjust = 0, size = 6) + scale_fill_manual(values = c(col))

  p3 <- p3 + theme_classic() + theme(axis.title  = element_text(size = 24),
          axis.text = element_text(size = 15))
  p3
     ggsave(p3, filename = "./output/figures/figS1.pdf", width = 11.5, height = 8)
```

>>>>

  # Lets now convert these to a %
    f_VR_mean_ef  <- abs((exp(f_VR_mean) - 1)*100) 
    m_VR_mean_ef  <- abs((exp(m_VR_mean) - 1)*100) 
    t_VR_mean_ef  <- abs((exp(t_VR_mean) - 1)*100)

@@

##################
  # Figure S1
################## 
  # Sensitivity analysis that looks at how variance changes but not controlling for the mean.
  col <- c("#0871B9", "#F3B40D", "#1BB908")
  p3 <- orchard_plot(model3.2, xlab = TeX("$lnVR_{Q_{10}}$"), mod = "habitat", group  = "record_num", weights = "prop", data = lnVRQ10_data, angle = 45, trunk.size = 5) +
              scale_x_discrete(labels = c("T" = "Terrestrial","M" = "Marine" ,"F" = "Freshwater")) + annotate("text", x = 1.3, y = -5.2, 
           label =TeX(paste0("$\\mu = $", round(mean(f_VR_mean), 2), " [", round(quantile(f_VR_mean, 0.025), 2)," to ", round(quantile(f_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
  annotate("text", x = 1.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(f_VR_mean), digit = 2)))), hjust = 0, size = 6) + 
  annotate("text", x = 1.15, y = -5, 
           label =paste0(round(mean(exp(f_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + 
  annotate("text", x = 2.3, y = -5.2, 
           label =TeX(paste0("$\\mu = $", round(mean(m_VR_mean), 2), " [", round(quantile(m_VR_mean, 0.025), 2)," to ", round(quantile(m_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
  annotate("text", x = 2.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(m_VR_mean), digit = 2)))), hjust = 0, size = 6) + 
  annotate("text", x = 2.15, y = -5, 
           label =paste0(round(mean(exp(m_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + annotate("text", x = 3.3, y = -5.2, 
           label =TeX(paste0("$\\mu = $", round(mean(t_VR_mean), 2), " [", round(quantile(t_VR_mean, 0.025), 2)," to ", round(quantile(t_VR_mean, 0.975),2), "] ")), hjust = 0, size = 6) + 
  annotate("text", x = 3.15, y = -5, 
           label =paste0(round(mean(exp(t_VR_mean)-1)*100, 2), "%"), hjust = 0, size = 6) + labs(shape = "Type") +
    annotate("text", x = 3.15, y = -3.5, label = TeX(paste0("$\\italic(p)$ ", p_value(round(pmcmc(t_VR_mean), digit = 3)))), hjust = 0, size = 6) + scale_fill_manual(values = c(col))

  p3 <- p3 + theme_classic() + theme(axis.title  = element_text(size = 24),
          axis.text = element_text(size = 15), legend.text = element_text(size = 15),
          legend.title = element_text(size = 15))

  ggsave(p3, filename = "./output/figures/figS1.pdf", width = 10, height = 8)

  figs1 <- image_read("./output/figures/figS1.pdf")
  figs1
```
